sem

### 2022-12-09 scripts/workshop/sem.Rmd
look at sem more in depth

library(tidyverse)
library(magrittr)
library(piecewiseSEM)
library(nlme)
library(lmerTest)

@@

@@

```{r}
dSep(sem)
summary(sem)
```
Lefcheck example

>>>>

library(tidyverse)
library(magrittr)
library(piecewiseSEM)
library(nlme)
library(lmerTest)
library(dagitty)

@@

```{r}
prev_mod <- dagitty("dag{
  temp -> cc
  temp -> size
  cc -> prev
  size -> prev
  temp -> prev
             }")

plot(graphLayout(prev_mod))

```

@@

```{r}
basisSet(sem)
dSep(sem, conditioning = T)
fisherC(sem)
coefs(sem, intercepts = T)
rsquared(sem)
```

```{r}
summary(sem)
plot(sem)
plot(sem, return = T)
```

Lefcheck example
